Synthesis of Solar Photovoltaic Systems: Optimal Sizing Comparison\thanks{Supported by Newton Fund (ref. 261881580) and FAPEAM (Amazonas State Foundation for Research Support, calls 009/2017 and PROTI Pesquisa 2018).}

### 2020-04-23 Tex/CAV2019/Trindade_Cordeiro_VSTTE2020.tex
Revised Section 4.6
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

The results are presented at Table~\ref{tab1}.

@@

We have reported a favourable assessment of the proposed method. Nevertheless, we have also identified three threats to the validity of our results that constitute future work: (1) improvement of the power reliability analysis: to include loss of load probability or loss of power supply probability, which can make the analysis more accurate; (2) improvement of the system cost analysis by including operational and maintenance costs to the adopted LCC analysis; and (3) to increase the equipment and manufacturers database: this will increase the optimization complexity, but the result will also allow improved sizing.

>>>>

The results are presented in Table~\ref{tab1}.

@@

We have reported a favourable assessment of the proposed method. Nevertheless, we have also identified four threats to the validity of our results that constitute future work: (1) improvement of the power reliability analysis: to include loss of load probability or loss of power supply probability, which can make the analysis more accurate; (2) improvement of the system cost analysis by including operational and maintenance costs to the adopted LCC analysis; (3) to increase the equipment and manufacturers database: this will increase the optimization complexity, but the result will also allow improved sizing; and (4) the underlying symbolic verifiers employed here perform bit-precise verification based on the Floating-Point (FP) theory; we could use a real arithmetic strategy to tackle these equations; however, in this study, we have exploited the FP arithmetic, which is an approximation of the real one.
